Endogenous Politics and \\ the Design of Trade Institutions

### 2017-01-02 to-do.tex
add old misc notes; MRC WP result and next steps

				\end{itemize}
			\item Mostafa, Nuno, Giovanni, Anson to some extent: Cardinal vs. ordinal
				\begin{itemize}
					\item Giovanni: if I can show properties survive  monotonic transformation, I'm fine
					\item They don't like gov't choosing its own preferences. May just need to change wording
				\end{itemize}
			\item Bob: what is fundamental structure of preferences?
			\item The way $e$ affects preferences doesn't change!!! Preferences are wrapped up in $\ga$!
				\begin{itemize}
					\item ``How the assumption of a non-unitary legislature translates into this incentive constraint. In the non-unitary legislature, if the current period incentive constraint includes any future value of lobbying effort, this would mean the current-period median legislator evaluating her current-period incentive constraint using a mixture of her own political-economy weight with those of the legislators who are median in the future in the trade agreement and trade-war scenarios. The first major step I have taken to clarify the incentive constraint is the analysis in Appendix B.1 of the unitary model (described above), which I would guess is the model you had in mind. I discuss the differences between the unitary and non-unitary models in the beginning of that Appendix.''
					\item ``Note that the median legislator, whose identity is determined by the lobby's effort level $e_b$, evaluates future payoffs according to her own political economy weight, $\ga(e_b)$. Of course, depending on legislator $e_b$'s choice, either legislator $e_a$ or legislator $e_{tw}$ will be the decision maker in those future periods. But legislator $e_b$, who is the decision maker in the current period, maximizes her own welfare given the predicted behavior of future decision makers.''

@@

		\item I like the way you use Bagwell and Staiger (2005) as your benchmark.  But I also wondered whether Maggi and Rodriguez-Clare (2007, henceforth MRC) also offered a useful benchmark.  I know you did have comparisons to their paper in many places but it would be useful if this could be more systematic, and if your paper could draw careful parallels to your assumptions and theirs.  In both papers, the government wants to set a tariff cap in order to be able to extract rents from lobbies afterwards.  But your mechanisms seem quite different.  They have capital mobility whereas your factors are specific to each sector.  If capital is highly immobile they have a hold-up problem, which creates an incentive for lobbies to try to prevent too much liberalization under the agreement.  What drives this feature in your model?  Here I think it would be useful to explain carefully the sequence of events in your set-up more carefully.  What is the relationship between lobby effort level and tariff policy?  Is effort fixed first, after which the government sets its tariff?  If so it seems to me that would drive a kind of hold-up because lobbying effort is sunk.  It would be useful to be clearer about this so we can really understand where the results are coming from and how they compare to MRC.  Having done that, you could bring in ex-ante lobbying and treat it the same way. 
		\item In general it seems to me that you seem to "dependent" on Bagwell and Staiger... (e.g. beginning of Sections 4 and 6).

@@

@@

				\item Shift all bargaining power to gov't. They do this in WP version. Read to see what their result is for $z=0$.

@@

@@

\section{Numeraire}
Do I need to add a numeraire so I can put $e$ in terms of it?

@@

\section{More on escape clause / WEC}
			\item The part I really liked was when you analysed the exogenous and endogenous effects on gamma simultaneously around page 28.  In fact I was itching to get to that part right from when you discussed it in the introduction.  
					\item The paper makes the extremely important point almost in passing.  I would be interested to see a more detailed examination of how this works.  It's particularly interesting that in the presence of a shock the governments will use the escape clause as intended but without a shock a lobby group would always `step into the breach' and cause it to be abused.  I would like to see the paper devote more attention to the conditions under which this problem arises and when it does not.
					\item Then the paper begins to address the equally important question of what can be done about this problem, but again stops short of providing a really compelling answer.  I think it would be worth exploring this in detail.  The paper does get to the \textbf{heart of the issue, which is that `s' can be observed by the DSB but e cannot}.  Get to the bottom of how to design a dispute settlement system that resolves the conflict created by `e vs s'.
			\item `Withdrawal of equivalent concessions' (WEC).
					\item Zissimos (2007): a government \textbf{`chooses the severity of its own punishment'} by the extent of its initial deviation. I'm wondering whether your framework offers an answer for why WEC made sense as an approach to punishment.
					\item Under WEC, it is worth deviating from the agreement in proportion to $s$ because your partner deviates to the same extent and that keeps the agreement on track; the point first made by Bagwell and Staiger (1990).
					\item But WEC might eliminate the incentive to respond to lobbying pressure $e$ because when your trade partner deviates by WEC this takes away from you exactly (in a symmetrical framework) what you gained from the lobby for implementing a deviation of that size.
							\item \textbf{Think about how WEC may mitigate LOBBY'S incentives through reaction of gov't}
							\item Ben doesn't have any need for escape; have to put WEC into my framework
							\item Government feels $\ga$ the same whether it's elevated because of $s$ or $e$
							\item What is the neutralizing that happens? Why would the government invoke EC when it knows that WEC is coming anyway? Because it's in another sector where it puts less weight right now?
							\item WEC should work against TOT, not PE shock?
					\item I would find an examination of WEC much more compelling that the approach to punishment that you currently discuss on page 20, whereby two bindings are negotiated.
					\item I say I'm going to do this on Page 27. Need to decide and either do it or take this out.
			\item Puzzle to explain: WEC has an effect here, and that effect is weakened by the change in EC rules during the Uruguay Round, even though no retaliation for 3 yrs
					\item ``Why Are Safeguards under the WTO So Unpopular?'' (World Trade Review 2002), %\url{C:\Users\Kristy\Dropbox\Research\PEshocks\Literature\2016}
					\item Need to understand better what changed, both with safeguard and with other policy instruments
					\item Note that safeguards agreement states that safeguard can only be at level necessary to remedy injury, and must liberalize as possible
					\item \textbf{perhaps better able to respond to $\ga(e)$ before dispute settlement?}
							\item Lack of effective enforcement before WTO?
			\item What does WTO \textit{really} want? To discourage rent-seeking lobbying but allow governments to escape when there's a real shock.
					\item There may be legitimate lobbying to communicate about the shock, so can't look at the presence of lobbying as a sufficient statistic
			\item Need to go to continuous value of EC tariff
					\item There will be optimal tariff for whatever value of $s$ is realized
							\item Not sure how fine I want to go with $s$
					\item Lobby will choose its optimal level of $e$. Will this be constrained in any way? Probably not, if there isn't a fixed EC-binding.
			\item After $s$ realized, $e$ choosen by lobby. Then government can choose $\tau$
				\begin{enumerate}
					\item consistent with $s$, no retaliation
					\item consistent with $s$ and $e$ and be retaliated against according to WEC (need to work WEC into model--repeated game incentives necessary)
							\item Is responding to $e$ in some cases worth it?
							\item Does WEC help or hurt vs. grim trigger, $T$ period Nash reversion?
				\end{enumerate}

\section{Costly state verification}
		\begin{itemize}
				\item Have you seen the work that Beshkar and Bond have done on what they call `contingent protection'?  I can't remember if they are drawing on the work of other people when they refer to the escape clause as `costly state verification.'  This seems to provide an alternative way of separating genuine shocks from those created by lobby groups.  How does your approach relate to costly state verification?
				\item I say that I'm going to provide a result along the lines of Beshkar 2010b. Same or different from costly state verification? Which is more helpful?
		\end{itemize}

>>>>

				\end{itemize}
			\item Mostafa, Nuno, Giovanni, Anson to some extent: Cardinal vs. ordinal
				\begin{itemize}
					\item Giovanni: if I can show properties survive  monotonic transformation, I'm fine
					\item They don't like gov't choosing its own preferences. May just need to change wording
				\end{itemize}
			\item Bob: what is fundamental structure of preferences?
			\item The way $e$ affects preferences doesn't change!!! Preferences are wrapped up in $\ga$!
				\begin{itemize}
					\item ``How the assumption of a non-unitary legislature translates into this incentive constraint. In the non-unitary legislature, if the current period incentive constraint includes any future value of lobbying effort, this would mean the current-period median legislator evaluating her current-period incentive constraint using a mixture of her own political-economy weight with those of the legislators who are median in the future in the trade agreement and trade-war scenarios. The first major step I have taken to clarify the incentive constraint is the analysis in Appendix B.1 of the unitary model. I discuss the differences between the unitary and non-unitary models in the beginning of that Appendix.''
					\item ``Note that the median legislator, whose identity is determined by the lobby's effort level $e_b$, evaluates future payoffs according to her own political economy weight, $\ga(e_b)$. Of course, depending on legislator $e_b$'s choice, either legislator $e_a$ or legislator $e_{tw}$ will be the decision maker in those future periods. But legislator $e_b$, who is the decision maker in the current period, maximizes her own welfare given the predicted behavior of future decision makers.''

@@

		\item I like the way you use Bagwell and Staiger (2005) as your benchmark.  But I also wondered whether Maggi and Rodriguez-Clare (2007, henceforth MRC) also offered a useful benchmark.  I know you did have comparisons to their paper in many places but it would be useful if this could be more systematic, and if your paper could draw careful parallels to your assumptions and theirs.  In both papers, the government wants to set a tariff cap in order to be able to extract rents from lobbies afterwards.  But your mechanisms seem quite different.  They have capital mobility whereas your factors are specific to each sector.  If capital is highly immobile they have a hold-up problem, which creates an incentive for lobbies to try to prevent too much liberalization under the agreement.  What drives this feature in your model?  Here I think it would be useful to explain carefully the sequence of events in your set-up more carefully.  What is the relationship between lobby effort level and tariff policy?  Is effort fixed first, after which the government sets its tariff?  If so it seems to me that would drive a kind of hold-up because lobbying effort is sunk.  It would be useful to be clearer about this so we can really understand where the results are coming from and how they compare to MRC. 
		\item In general it seems to me that you seem to ``dependent" on Bagwell and Staiger... (e.g. beginning of Sections 4 and 6).

@@

				\item Contingent payments are hard to reconcile with uncertainty

@@

						\item Page 26-28 of working paper has government with all the bargaining power (and no capital mobility, but remember that the capital owners choose where to invest in the first period). Here, could be free trade but could be interior to get some rents.

@@

						\item Or rather, should I follow Limao and Tovar?

@@

\section{Numeraire}
Do I need to add a numeraire so I can put $e$ in terms of it?
\begin{itemize}
	\item Does DGH97 or similar have it?
\end{itemize}

@@

\section{More on escape clause / WEC}
		\begin{itemize}
			\item The part I really liked was when you analysed the exogenous and endogenous effects on gamma simultaneously around page 28.  In fact I was itching to get to that part right from when you discussed it in the introduction.  
				\begin{itemize}
					\item The paper makes the extremely important point almost in passing.  I would be interested to see a more detailed examination of how this works.  It's particularly interesting that in the presence of a shock the governments will use the escape clause as intended but without a shock a lobby group would always `step into the breach' and cause it to be abused.  I would like to see the paper devote more attention to the conditions under which this problem arises and when it does not.
				\end{itemize}
			\item `Withdrawal of equivalent concessions' (WEC).
				\begin{itemize}
					\item Zissimos (2007): a government \textbf{`chooses the severity of its own punishment'} by the extent of its initial deviation. I'm wondering whether your framework offers an answer for why WEC made sense as an approach to punishment.
					\item Under WEC, it is worth deviating from the agreement in proportion to $s$ because your partner deviates to the same extent and that keeps the agreement on track; the point first made by Bagwell and Staiger (1990).
					\item But WEC might eliminate the incentive to respond to lobbying pressure $e$ because when your trade partner deviates by WEC this takes away from you exactly (in a symmetrical framework) what you gained from the lobby for implementing a deviation of that size.
						\begin{itemize}
							\item \textbf{Think about how WEC may mitigate LOBBY'S incentives through reaction of gov't}
							\item Ben doesn't have any need for escape; have to put WEC into my framework
							\item Government feels $\ga$ the same whether it's elevated because of $s$ or $e$
							\item What is the neutralizing that happens? Why would the government invoke EC when it knows that WEC is coming anyway? Because it's in another sector where it puts less weight right now?
							\item WEC should work against TOT, not PE shock?
						\end{itemize}
					\item I would find an examination of WEC much more compelling that the approach to punishment that you currently discuss on page 20, whereby two bindings are negotiated.
					\item I say I'm going to do this on Page 27. Need to decide and either do it or take this out.
				\end{itemize}
			\item Puzzle to explain: WEC has an effect here, and that effect is weakened by the change in EC rules during the Uruguay Round, even though no retaliation for 3 yrs
				\begin{itemize}
					\item ``Why Are Safeguards under the WTO So Unpopular?'' (World Trade Review 2002), %\url{C:\Users\Kristy\Dropbox\Research\PEshocks\Literature\2016}
					\item Need to understand better what changed, both with safeguard and with other policy instruments
					\item Note that safeguards agreement states that safeguard can only be at level necessary to remedy injury, and must liberalize as possible
					\item \textbf{perhaps better able to respond to $\ga(e)$ before dispute settlement?}
						\begin{itemize}
							\item Lack of effective enforcement before WTO?
						\end{itemize}
				\end{itemize}
			\item What does WTO \textit{really} want? To discourage rent-seeking lobbying but allow governments to escape when there's a real shock.
				\begin{itemize}
					\item There may be legitimate lobbying to communicate about the shock, so can't look at the presence of lobbying as a sufficient statistic
				\end{itemize}
			\item Does WEC help or hurt vs. grim trigger, $T$ period Nash reversion?
		\end{itemize}

\section{Costly state verification}
		\begin{itemize}
				\item Have you seen the work that Beshkar and Bond have done on what they call `contingent protection'?  I can't remember if they are drawing on the work of other people when they refer to the escape clause as `costly state verification.'  This seems to provide an alternative way of separating genuine shocks from those created by lobby groups.  How does your approach relate to costly state verification?
				\item I say that I'm going to provide a result along the lines of Beshkar 2010b. Same or different from costly state verification? Which is more helpful?
				\item Need to check this for sure in new section. I don't have cost to verification.
		\end{itemize}
